---
title: "Using Regular Expressions"
output: html_notebook
---

```{r}
library(tidyverse)
library(dcData)
```


```{r}
NameList <- BabyNames %>% group_by(name, sex) %>% summarise(total=sum(count)) %>% arrange(desc(total))
```

### Problem 17.1

#### Boys’ names ending in a vowel.

```{r}
BabyNames %>% filter(grepl("[aeiou]$", name)) %>% filter(sex=="M") %>% group_by(name) %>% summarise(total=sum(count)) %>% arrange(desc(total)) %>% head(10)
```

They are
* George
* Joshua
* Kyle
* Lawrence
* Joe
* Willie
* Jesse
* Bruce
* Eugene

#### Names with a space (like Lee Ann)
```{r}
BabyNames %>% filter(grepl("\\w+ \\w+ ", name))
```
There are no name in BabyNames with a space.

#### Names ending with “joe” (like BettyJoe)

```{r}
BabyNames %>% filter(grepl("*joe$", name, ignore.case = TRUE)) %>% group_by(name) %>% summarise(total=sum(count)) %>% arrange(desc(total))
```

There are only 7 name with end with "joe": Joe, Billyjoe, Bobbyjoe, Marjoe, Billiejoe, Maryjoe, Johnnyjoe


### Problem 17.3
It is phone number.

There are 3 components are extracted:
([2-9][0-9]{2}) - It must be 3 letters. The first letter is one of digit from 2 to 9. The remain two letter could be any number between 0 to 9.
([0-9]{3}) - It must be 3 letters. Each letter could be any number from 0 to 9.
([0-9]{4}) - It must be 4 letters. Each letter could be any number from 0 to 9.



### Problem 17.4

1. How long will the strings be that match the pattern?
2 characters length will match the patter. For example: AL

2. How many different strings will match?
50?

3. People living in the United States may be able to figure out what the pattern is meant to express. Give it a try.
It looks the abbreviation of States.

### Problem 17.5
```{r}
BibleNames <- readr::read_csv("https://mdbeckman.github.io/dcSupplement/data/BibleNames.csv")
BibleNames %>% filter(grepl("bar|dam|lory", name, ignore.case = TRUE))
BibleNames %>% filter(grepl("(bar|dam|lory)$", name, ignore.case = TRUE))

```

1. There are 32 names contains bar, dam and lory.
2. There are 6 names end with these words

### Problem 17.7
```{r}
BabyWithBibleName <- BabyNames %>% group_by(name) %>% summarise(total=sum(count)) %>% inner_join(BibleNames) %>% arrange(desc(total)) 
BabyWithBibleName %>% head(10)
```

The ten most poupular name related with Bible name are:
James, John, Mary, David, Joseph, Thomas, Daniel, Paul, Mark, Andrew.

