---
title: "Statistics of Gene Expression"
output: html_notebook
---

```{r}
library(tidyverse)
library(dcData)
```

```{r}

Narrow <- NCI60 %>% pivot_longer(-Probe, names_to="cellLine", values_to="expression")
CellType <- NCI60cells %>% select(cellLine, tissue) %>% mutate(cellLine=gsub("\\:",".",cellLine))
Narrow <- Narrow %>% inner_join(CellType)


```

```{r}
Probe_TOP3A <- Narrow %>% filter(Probe=="TOP3A")

#exp() function in R Language is used to calculate the power of e i.e. e^y or we can say exponential of y. The value of e is approximately equal to 2.71828….. Parameters: y: It is any valid R number either positive or negative
SummaryStats <- Probe_TOP3A %>% group_by(tissue) %>% summarise(mn_expr = exp(mean(expression, na.rm = TRUE)))

#"The heights of the bars commonly represent one of two things: either a count of cases in each group, or the values in a column of the data frame. By default, geom_bar uses stat="bin". This makes the height of each bar equal to the number of cases in each group, and it is incompatible with mapping values to the y aesthetic. If you want the heights of the bars to represent values in the data, use stat="identity" and map a value to the y aesthetic."

SummaryStats %>% ggplot(aes(x=tissue, y= mn_expr)) + geom_bar(stat = "identity") + theme(axis.text.x = element_text(angle = 30, hjust=1))

```

```{r}
Probe_TOP3A %>% ggplot(aes(x=tissue, y= exp(expression))) + geom_point() + theme(axis.text.x = element_text(angle = 30, hjust=1))

```

The bar chart only express the mean value. It doesn't reflect the distribution. I would suggest to use boxplot.

1. Lighten up on the color. Perhaps alpha = 0.2, or maybe a dot plot rather than a bar chart.

```{r}
SummaryStats %>% ggplot(aes(x=tissue, y= mn_expr)) + geom_bar(stat = "identity", alpha=0.2) + theme(axis.text.x = element_text(angle = 30, hjust=1))

```

```{r}
SummaryStats %>% ggplot(aes(x=tissue, y= mn_expr)) + geom_point() + theme(axis.text.x = element_text(angle = 30, hjust=1))
```

2. Reorder the tissue types.

```{r}
SummaryStats_reorder <- SummaryStats %>% mutate(tissue=reorder(tissue, mn_expr))

```

3. Show a statistical measure of the variation.
```{r}
SummaryStats_se <- Probe_TOP3A %>% group_by(tissue) %>% summarise(mn_expr=mean(expression, na.rm = TRUE), se=sd(expression, na.rm = TRUE)/sqrt(n()))
SummaryStats_se %>% ggplot(aes(x=tissue, y=se)) + geom_bar(stat = "identity") 
```



```{r}
SummaryStats %>% ggplot(aes(x=tissue, y=exp(mn_expr))) + geom_bar(stat = "identity", fill="gray", color=NA) + geom_point(data = Probe_TOP3A, aes(x=tissue, y=exp(expression))) + theme(axis.text.x = element_text(angle = 30, hjust = 1))
                                                                                                  
```


4. Show the expression value for each of the individual cases in Probe_TOP3A as seen in Figure 18.2 in order to display cell variability directly.
```{r}
Probe_TOP3A %>% ggplot(aes(x=tissue, y= expression)) + geom_point() + theme(axis.text.x = element_text(angle = 30, hjust=1))
```

5. Use a different modality: e.g. a dot plot; a box-and-whiskers plot (with notch = TRUE); a violin plot

```{r}
Probe_TOP3A %>% ggplot(aes(x=tissue, y= expression)) + geom_boxplot() + theme(axis.text.x = element_text(angle = 30, hjust=1))

```

```{r}
Probe_TOP3A %>% ggplot(aes(x=tissue, y= expression)) + geom_violin() + theme(axis.text.x = element_text(angle = 30, hjust=1))

```

TWo plot

```{r}
SummaryStats %>% 
  ggplot(aes(x = tissue, y = exp(mn_expr))) +
  geom_bar(stat = "identity", fill = "gray", color = NA) +
  geom_point(data = Probe_TOP3A, aes(x = tissue, y = exp(expression))) + 
  theme(axis.text.x = element_text(angle = 30, hjust = 1))
```

Top and Bottom

```{r}
SummaryStats_Top_Bottom <- 
  SummaryStats_se %>%
  mutate(top = mn_expr + 2 * se,
         bottom = mn_expr - 2 * se)

SummaryStats_Top_Bottom %>% ggplot(aes(x=tissue, y=exp(mn_expr))) + geom_bar(stat = "identity", alpha=0.2) + geom_errorbar(aes(x=tissue, ymax=exp(top), ymin=exp(bottom)), width=0.5) + theme(axis.text.x = element_text(angle = 30, hjust=1))
```

```{r}
SummaryStats_Top_Bottom %>% ggplot(aes(x=tissue, y=exp(mn_expr))) + geom_errorbar(aes(x=tissue, ymax=exp(top), ymin=exp(bottom)), width=0.5) + geom_point(data = Probe_TOP3A, aes(x=tissue, y=exp(expression))) + theme(axis.text.x = element_text(angle = 30, hjust=1))
```



### Your turn
I choose AT_D_3

```{r}
Probe_AT_D_3 <- Narrow %>% filter(Probe=="AT_D_3")
SummaryStat_SE_TB_AT_D_3 <- Probe_AT_D_3 %>% group_by(tissue) %>% summarise(mn_expr = mean(expression, na.rm = TRUE), se=sd(expression, na.rm = TRUE)/sqrt(n())) %>% mutate(top = mn_expr + 2 * se, bottom = mn_expr - 2 * se)

SummaryStat_SE_TB_AT_D_3 %>% ggplot(aes(x=tissue, y=exp(mn_expr))) + geom_errorbar(aes(x=tissue, ymax=exp(top), ymin=exp(bottom)), width=0.5) + geom_point(data = Probe_AT_D_3, aes(x=tissue, y=exp(expression))) + theme(axis.text.x = element_text(angle = 30, hjust=1))


```


### 18.12
```{r}
# customize a user-defined function called `r2`
r2 <- function(data) {
  mosaic::rsquared(lm(data$expression ~ data$tissue))
}

ProbeR2 <- 
  Narrow %>% 
  group_by(Probe) %>%
  dplyr::do(probe_rsq = r2(.)) %>%
  mutate(r2 = unlist(probe_rsq))

Actual <-
  ProbeR2 %>%
  arrange(desc(r2)) %>%
  head(30) 

Actual %>%
  ggplot(aes(x = reorder(Probe, desc(r2)), y = r2)) +
  geom_point() + 
  xlab("Probe") + 
  ylab("R-squared") + 
  ggtitle("Probes with large R-squared for expression level explained by tissue type") + 
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```


### Your turn

I choose CD53

```{r}
Probe_CD53 <- Narrow %>% filter(Probe=="CD53")
SummaryStat_SE_TB_CD53 <- Probe_CD53 %>% group_by(tissue) %>% summarise(mn_expr = mean(expression, na.rm = TRUE), se=sd(expression, na.rm = TRUE)/sqrt(n())) %>% mutate(top = mn_expr + 2 * se, bottom = mn_expr - 2 * se)

SummaryStat_SE_TB_CD53 %>% ggplot(aes(x=tissue, y=exp(mn_expr))) + geom_errorbar(aes(x=tissue, ymax=exp(top), ymin=exp(bottom)), width=0.5) + geom_point(data = Probe_CD53, aes(x=tissue, y=exp(expression))) + theme(axis.text.x = element_text(angle = 30, hjust=1))

```

Yes, it is very different. Some specific tissue has very different shape.

