---
title: "Graphics and Their Grammar"
output: html_notebook
---

Construct a graphics frame.
Add a layer of glyphs.
Set an axis label.
Divide the frame into facets.
Change the scale for the frame.

1. geom_point()
Add a layer of glyphs.

2. geom_histogram()
Add a layer of glyphs.

3. ggplot()
Construct a graphics frame.

4. scale_y_log10()
Construct a graphics frame.

5. ylab()
Set an axis label.

6. facet_wrap()
Divide the frame into facets.

7. geom_segment()
Add a layer of glyphs.

8. xlim()
Construct a graphics frame.

9. facet_grid()
Divide the frame into facets.

```{r}
library(mosaicData)
```

Problem 8.2 

```{r}

ggplot( data = CPS85, aes(x = wage)) + geom_density() + aes(fill = sex, alpha=0.5, show.legend = FALSE) + facet_wrap(~married, ncol = 4) + labs(title = "") + theme(legend.position = "right")
```


```{r}
CPS85_Wage_Age <- CPS85 %>% group_by(age, sex, married) %>% summarise(wage=mean(wage))
ggplot(data = CPS85_Wage_Age, aes(x = age, y = wage))+ ylim(0,15) + geom_point(alpha=0) + aes(colour = sex) + facet_grid(rows = vars(married))  + stat_smooth(method = loess) + theme(legend.position = "right") + labs(title = "") 
```
```{r}

CPS85_Sector <- CPS85 %>% group_by(age, sex, sector) %>% summarise(wage=mean(wage))
ggplot(data = CPS85_Sector, aes(x = age, y = wage)) + geom_point(alpha=0)  + aes(colour = sex) + facet_wrap(~sector, ncol = 3)  + stat_smooth(method = loess) + theme(legend.position = "right") + labs(title = "") 

```



Problme 8.3

A.
```{r}
ggplot(data = CPS85, aes(x = age, y = wage)) + geom_point()  + labs(title = "")
```

B.
```{r}
ggplot(data = CPS85, aes(x = age, y = wage, group=sex)) + geom_point(aes(shape=sex))  + labs(title = "") + theme(legend.position="top")
```
C.
```{r}
ggplot(data = CPS85, aes(x = age, y = wage, group=sex)) + geom_point(aes(shape=sex))  + facet_grid(rows = vars(married)) + labs(title = "") + theme(legend.position="top")

```

D.
```{r}
ggplot(data = CPS85, aes(x = age, y = wage, group=married)) + geom_point(aes(shape=married))  + labs(title = "") + theme(legend.position="top")
```
