---
title: "Chapter 13 Ranks"
output: html_notebook
---

```{r}
library(tidyverse)
library(dcData)

```


### Problem 13.1
```{r}
BabyNames %>% group_by(name, sex) %>% summarise(the_total=sum(count)) %>% group_by(sex) %>% filter(rank(desc(the_total))<=5) %>% arrange(sex, desc(the_total))
```

If you want to find the least popular names, using ascending order and make rank(the_total) <= 5 will not return any result. It is because there are too many name are least popular. Their rank result will but more than 5. So it return nothing by:

```{r}
BabyNames %>% group_by(name, sex) %>% summarise(the_total=sum(count)) %>% group_by(sex) %>% filter(rank(the_total)<=5)
```

You could refer the row_number
```{r}
BabyNames %>% group_by(name, sex) %>% summarise(the_total=sum(count)) %>% group_by(sex) %>% mutate(the_rank=rank(the_total),the_order=row_number(the_total)) %>% arrange(the_order) %>% view()
```


### Problem 13.2
Draw top 100 is messing. Intead of it, I draw top 5. Even top 5, there are more than 5.

```{r}
# This step is a bit slow. it returns top 100 names in each years

BabyNames_Top5_in_years <- BabyNames %>% group_by(name, year) %>% summarise(the_total=sum(count)) %>% group_by(year) %>% filter(rank(desc(the_total))<=5)

# Each year's baby numbers
Babies_in_years<-BabyNames %>% group_by(year) %>% summarise(total_in_years=sum(count))

# Top 100 baby names' fraction
Baby_top5_fraction_in_years <-BabyNames_Top100_in_years %>% left_join(Babies_in_years) %>% mutate(fraction_top100=the_total/total_in_years)

# Plot

Baby_top5_fraction_in_years %>% ggplot(aes(x=year, y=fraction_top100)) + geom_line(aes(color=name)) + ylab("Percentage") + labs(title = "Percentage vs year")
```

I just don't use pivot_wider at all. Not sure why?


### Problem 13.3


```{r}
# Return baby name once in top 50 popular names.
BabyNames_in_years <- BabyNames %>% group_by(name, year) %>% summarise(the_total=sum(count))
BabyName_top50_once <- BabyNames_in_years %>% group_by(year) %>% filter(rank(desc(the_total))<=50) %>% group_by(name) %>% distinct(name)


# Return baby name once in least popular name rank above 1000
BabyNames_least1000 <- BabyNames_in_years %>% group_by(year) %>% filter(rank(desc(the_total)) >1000) %>% group_by(name) %>% distinct(name)


# Return the share part with inner_join
BabyName_top50_once %>% inner_join(BabyNames_least1000)

```

There are 188 names meet the creteria.
