---
title: "Chapter 12 Wide versus Narrow Data"
output: html_notebook
---


```{r}
library(tidyverse)
library(dcData)
```
### Problem 12.1

1. Sex

```{r}
BothSexes <-
  BabyNames %>%
  pivot_wider(names_from = sex, values_from = count) %>%
  filter(M > 5 | F > 5)
```

2.
```{r}
BothSexes %>% mutate(gender_balance=abs(log(F/M))) %>% arrange(gender_balance) %>% head(10)
```

3. 
```{r}
BothSexes %>% filter(M>100 & F>100) %>% mutate(gender_balance=abs(log(F/M))) %>% arrange(gender_balance) %>% head(10)
```

4.  

```{r}

# Step 1. Get lasting popularity
BabyNames_Exceed_100_Every_Year <- BabyNames %>% group_by(name,year) %>% summarise(total=sum(count)) %>% filter(total>100)
BabyNames_lasting_popularity <- BabyNames_Exceed_100_Every_Year %>% group_by(name) %>% summarise(happen_times=n()) %>% filter(happen_times>20)

# Step 2. Get gender balance value for all babies
BabyNames_with_gender_balance_value <- BabyNames %>% pivot_wider(names_from = "sex", values_from="count", values_fill=0) %>% group_by(name) %>% summarise(F=sum(F),M=sum(M))%>% mutate(gender_balance=abs(log(F/M))) %>% arrange(gender_balance)

# Step 3. Get the final answer. One of the name is unknown which need to be removed.
BabyNames_lasting_popularity %>% left_join(BabyNames_with_gender_balance_value) %>% arrange(gender_balance) %>% filter(name !="Unknown") %>% head(10)
```

5. 
```{r}
BabyNames_happen_more_than_2 <- BabyNames %>% pivot_wider(names_from = "sex", values_from="count", values_fill=0) %>% mutate(gender_F_ratio=F/(F+M)) %>% group_by(name) %>% summarise(happy_times=n()) %>% filter(happy_times>1)


BabyName_F_Ratio <- BabyNames %>% pivot_wider(names_from = "sex", values_from="count", values_fill=0) %>% mutate(gender_F_ratio=F/(F+M))

BabyNames_happen_more_than_2 %>% left_join(BabyName_F_Ratio) %>% group_by(name) %>% summarise(gender_change=max(gender_F_ratio)-min(gender_F_ratio)) %>% arrange(desc(gender_change)) %>% head(1)

BabyName_F_Ratio %>% filter(name=="Aalijah") %>% ggplot(aes(x=year, y=gender_F_ratio)) + geom_line()

```

### Problem 12.2.
1. 
    Version 1 is narrow data
    Version 2 is wide data
    Version 3 is wide data

2. Version two is wider

`
Version_two = Version_one %>% pivot_wider(names_from = "sex"", values_from="nbabies"")
`

3. Version three is wider

`
Version_one = version_three %>% pivot_longer(c(1912,2012), names_to="year", values_to="nbabies")
`

4. Version two is better.

Version two could add one variable as gender ratio by mutate data verb.



5. No. You have to change it to version two.

### Problem 12.3.
1. 
* A versus C
    A is wider. 
    
* B versus C
    B is wider
    
* A versus B
    A is wider.
    
2. The answer B. 

    B %>% mutate(change=Y2001-Y2000)

3. The answer is C
    How to do it:
    a. C left join with ContinentData
    b. group_by(Continent, Year)
    c. summarise(total=sum(Value))


### Problem 4.

1. It is too narrow because the "when" column will vary from "subject", "before", "after". But subject is not a useful value for "when". So it is less useful when it convert to narrow form.

2.

BP_wide %>%
  pivot_longer(cols = c(before, after), 
               names_to = "when", values_to = "sbp")