---
title: "Chapter 16 Data Scraping and Intake Methods"
output: html_notebook
---

```{r}
library(tidyverse)
library(data.table)
library(rvest)
```


```{r}
web_url <- "https://mdbeckman.github.io/dcSupplement/data/houses-for-sale.csv"
MyDataTable <- read_csv(web_url)
MyDataTable %>% select(price, bedrooms, bathrooms, fuel, air_cond, construction)

```

```{r}
file_name <- file.choose()
MyDataTable2 <- fread(file_name) %>% as.data.frame()

```

```{r}
web_page <- "https://en.wikipedia.org/wiki/Mile_run_world_record_progression"
SetOfTables <- web_page %>% read_html() %>% html_nodes(css="table") %>% html_table(fill=TRUE)
Table1 <- SetOfTables[[0]]
```


### Problem 16.1
```{r}
lubridate::mdy("April 30, 1777")
lubridate::mdy("06-23-1912")
lubridate::dmy("3 March 1847")
lubridate::mdy_hm("Nov. 11th, 1918 at 11:00 am")
lubridate::mdy("July 20, 1969")
```


### Problem 16.2

1. "42,659.30" 
* as.numeric() can't convert the string to a numeric value
* readr::parse_number() can convert the string to a numeric value

2. "17%"
* as.numeric() can't convert the string to a numeric value
* readr::parse_number() can convert the string to a numeric value but the answer is wrong (17, the correct answer should be 0.17)

3. "Nineteen"
* Both can't convert the string to a numeric value

4. "£100"
* as.numeric() can't convert the string to a numeric value
* readr::parse_number() can convert the string to a numeric value

5. "9.8 m/seconds-square"
* as.numeric() can't convert the string to a numeric value
* readr::parse_number() can convert the string to a numeric value

6. "9.8 m/s^2"
* as.numeric() can't convert the string to a numeric value
* readr::parse_number() can convert the string to a numeric value

7. "6.62606957 × 10^-34 m2 kg / s"
* as.numeric() can't convert the string to a numeric value
* readr::parse_number() can convert the string to a numeric value but the answer is wrong (6.62607, the correct answer should be 6.62607e-34)


8. "6.62606957e-34"
* Both can convert the string to a numeric value

9. "42.659,30" (A European style)
* as.numeric() can't convert the string to a numeric value
* readr::parse_number() can convert the string to a numeric value

### Problem 16.3


```{r}
library(rvest)
library(lubridate)

web_page <- "http://en.wikipedia.org/wiki/Mile_run_world_record_progression"
SetOfTables <- web_page %>% read_html() %>% html_nodes(css = "table") %>% html_table(fill = TRUE)
Table4 <- SetOfTables[[4]]
Record_table4 <- Table4 %>% mutate(time_sec=as.duration(ms(Time)), Date_happen= dmy(gsub("\\[.\\]$", "", Date)))
                                   
Record_table4 %>% ggplot(aes(x=Date_happen, y=time_sec)) + geom_point() + geom_text(aes(label=Athlete))
```


